The `forestecology` R package for modeling interspecies competition between trees

### 2021-02-02 etc/paper/forestecology.Rmd
Ugly first stab at new abstract

>>>>

When modeling growth of trees, the effect of interspecies competition is often included.

We present the `forestecology` package providing methods .

Using R's S3 object-oriented system, we implement a class and methods for a specific linear, Bayesian neighborhood competition model of tree growth. Furthermore, this model can be cast in a permutation test framework to evaluate a null hypothesis of no impact of competitor species' identity

The package is setup such that it can be easily extended to other models.

The package follows a tidyverse-like structure whereby verb-named functions can be "piped" to form the sequence of steps of analysis from start to finish. Furthermore, most inputs/outputs are of `sf` class from the simple features package, thereby facilitating all wrangling and visualization of geospatial data.

We leverage the ForestGEO network's data collection protocols and standardized data formatting to ensure cross-site compatibility of analysis. We apply our model to the Smithsonian Conservation Biology Institute's large forest dynamics plot.
